Notes about Spin and TR Symmetry

### 2016-10-20 Notes about TR symmetry/Notes about TR symmetry.tex
My C.V..

        \paragraph{Implications for crystal systems} The above result has
        profound implications for crystal with zero spin.
        \begin{thm}
            For crystal with zero spin, one has in crystal momentum space,
            always at least a double degeneracy, except for certain point
            symmetric to $k$ and $-k$.
        \end{thm}
        \begin{proof}
            By equation \ref{eq:TRoper.trInCry.trInSpinless.hk}, one has
            $\phi(k)$ and $T\phi(k)$ corresponding to eigenstate in
            $k$ and $-k$. When $T$ acts on a wavefunction, its
            creation operator is affected and its ... (paused here).
        \end{proof}

>>>>

        \begin{remark}[Implications for crystal systems]
            By equation \ref{eq:TRoper.trInCry.trInSpinless.hk}, one has
            $\phi(k)$ and $T\phi(k)$ corresponding to two eigenstate in
            $k$ and $-k$. But since $\bra{\alpha}\ket{T\alpha}$ is not
            necessarily $0$ for $T^2= \mathbbm{1}$, We cannot prove
            that we have a double generacy because the two candidate
            $h(k)$ and $h(-k)$ might be the same wave function.
        \end{remark}

        Another important implication is that
        \begin{thm}
            Hall Conductance vanishes for Spinless time
            symmetric system.  
        \end{thm}
        \begin{proof}
            Recall for 
        \end{proof}
